---
output: html_document
editor_options: 
  chunk_output_type: console
format:
  html:
    html-table-processing: none
---

# Inventories {.unnumbered}

```{r packages and functions}
#| include: false
library(tidyverse)
library(gt)
library(yaml)
source("script/utils.R")
options(readr.show_col_types = FALSE)

params <- read_yaml("data/config.yml")

print_inventory <- function(ref, pattern, cols, return_tibble = FALSE) {
  tbl_inventory <- 
    read_rds("data_generated/works.rds") %>%
      left_join(
        read_csv("data/catalogue_overview.csv") %>% distinct(group, file),
        by = "group"
      ) %>%
      unite(group:number, col = "id", sep = ".", na.rm = TRUE) %>%
      mutate(id = str_glue("[{id}](/groups/{file}.html#work-{id})")) %>%
      separate_longer_delim(inventories, ", @") %>%
      filter(str_detect(inventories, ref)) %>%
      rowwise() %>%
      mutate(
        entries =
          str_match_all(inventories, pattern)[[1]] %>%
          magrittr::set_colnames(c("match", cols)) %>%
          as_tibble() %>%
          select(!match) %>%
          list()
      ) %>%
      unnest(entries) %>%
      select(all_of(cols), id) %>% 
      mutate(across(!id, parse_guess)) %>%
      arrange(pick(!id))
  
  if (return_tibble)
    return(tbl_inventory)
  
  tbl_inventory %>% 
    summarise(.by = all_of(cols), id = str_flatten_comma(id)) %>% 
    arrange(across(all_of(cols), \(c) str_rank(c, numeric = TRUE))) %>% 
    gt() %>%
    fmt_markdown(columns = id) %>%
    cols_label(id = params$catalogue_prefix) %>% 
    tab_options(
      column_labels.font.weight = "bold",
      table.align = "left",
      table_body.hlines.style = "none"
    )
}
```



## Historic

### @BrtniceInv

```{r Brtnice}
#| echo: false
#| output: asis
print_inventory(
  "BrtniceInv",
  pattern = "p. (\\w+), no. (\\w+)",
  cols = c("p.", "no.")
)
```


### @EsterhazyInv1812

```{r Esterhazy 1812}
#| echo: false
#| output: asis
print_inventory(
  "EsterhazyInv1812",
  pattern = "([\\w\\s]+) no. ([\\w-]+)",
  cols = c("genre", "no.")
)
```


### Herzogenburg

```{r A-H setup}
#| echo: false

works <-
  read_rds("data_generated/works.rds") %>% 
  unnest(sources, names_sep = "_") %>% 
  filter(str_starts(sources_source, "A-H ")) %>%
  left_join(
    read_csv("data/catalogue_overview.csv") %>% distinct(group, file),
    by = "group"
  ) %>%
  unite(group:number, col = "TumW", sep = ".", na.rm = TRUE) %>%
  select(number = sources_source, TumW, file) %>%
  mutate(number = str_replace(number, "A-H ", "")) %>%
  separate_longer_delim(number, ", ")

table_data <-
  read_csv("data/inventory_herzogenburg_works.csv") %>% 
  mutate(
    inv_a = str_glue("A.{section_1751}.{number_1751}"),
    inv_b = str_glue("B.{section_1774}.{number_1774}")
  ) %>%
  separate_longer_delim(shelfmark, delim = " | ") %>% 
  left_join(
    works %>% select(inv_a = number, TumW_a = TumW),
    by = "inv_a"
  ) %>%
  left_join(
    works %>% select(inv_b = number, TumW_b = TumW),
    by = "inv_b"
  ) %>%
  left_join(
    works %>% select(shelfmark = number, TumW_s = TumW),
    by = "shelfmark"
  ) %>%
  rowwise() %>%
  mutate(
    is_error = any(
      !is.na(shelfmark) &
        is.na(TumW_s),
      is.na(shelfmark) &
        !is.na(section_1751) &
        is.na(TumW_a),
      is.na(shelfmark) &
        !is.na(section_1774) &
        is.na(TumW_b),
      is.na(shelfmark) &
        !is.na(section_1751) &
        !is.na(section_1774) &
        TumW_a != TumW_b
    )
  ) %>%
  mutate(TumW = coalesce(TumW_s, TumW_a, TumW_b)) %>%
  left_join(
    works %>% distinct(TumW, file),
    by = "TumW"
  ) %>%
  mutate(TumW = str_glue("[{TumW}](/groups/{file}.html#work-{TumW})"))

if (any(table_data$is_error)) {
  print(table_data %>% filter(is_error))
  error("Problems found in A-H inventory")
}

n_works_1751 <- 
  table_data %>%
  filter(!is.na(section_1751)) %>%
  distinct(section_1751, page_1751, number_1751) %>%
  nrow()

n_works_1774 <- 
  table_data %>%
  filter(!is.na(section_1751)) %>%
  distinct(section_1751, page_1751, number_1751) %>%
  nrow()

n_works_extant <- 
  table_data %>%
  filter(!is.na(shelfmark)) %>%
  distinct(shelfmark) %>%
  nrow()
```

The two historic inventories of Stift Herzogenburg [@HerzogenburgInvA; @HerzogenburgInvB] contain `{r} n_works_1751` and `{r} n_works_1774` entries describing Tůma's works, respectively. However, only `{r} n_works_extant` works are extant.

```{r A-H inventories}
#| echo: false
#| output: asis

table_data %>% 
  select(!c(inv_a:TumW_s, is_error, file)) %>%
  gt() %>%
  tab_spanner("inventory 1751 (A)", columns = ends_with("1751")) %>% 
  tab_spanner("inventory 1774 (B)", columns = ends_with("1774")) %>% 
  cols_label(
    starts_with("section") ~ "section",
    starts_with("page") ~ "p.",
    starts_with("number") ~ "no."
  ) %>%
  cols_align("right") %>% 
  fmt_markdown(columns = TumW) %>% 
  sub_missing(missing_text = "") %>%
  tab_options(
    column_labels.font.weight = "bold",
    table_body.hlines.style = "none"
  )
```

In the table above, sections in the 1751 inventory have been consecutively numbered as follows:

```{r A-H inventory 1751 sections}
#| echo: false
#| output: asis

read_csv("data/inventory_herzogenburg_1751.csv") %>% 
  unite(from, to, col = "pp.", sep = "–") %>% 
  gt() %>%
  cols_align("right", columns = "pp.") %>%
  sub_missing(missing_text = "") %>%
  tab_options(
    column_labels.font.weight = "bold",
    table_body.hlines.style = "none"
  )
```

Likewise, sections in the 1774 inventory have been consecutively numbered as follows:

```{r A-H inventory 1774 sections}
#| echo: false
#| output: asis

read_csv("data/inventory_herzogenburg_1774.csv") %>% 
  unite(from, to, col = "fol.", sep = "–") %>% 
  gt() %>%
  cols_width("fol." ~ px(90)) %>%
  cols_align("right", columns = "fol.") %>%
  sub_missing(missing_text = "") %>%
  tab_options(
    column_labels.font.weight = "bold",
    table_body.hlines.style = "none"
  )
```


### Klosterneuburg

```{r A-KN setup}
#| echo: false

works <-
  read_rds("data_generated/works.rds") %>% 
  unnest(sources, names_sep = "_") %>% 
  filter(str_starts(sources_source, "A-KN ")) %>%
  left_join(
    read_csv("data/catalogue_overview.csv") %>% distinct(group, file),
    by = "group"
  ) %>%
  unite(group:number, col = "TumW", sep = ".", na.rm = TRUE) %>%
  select(number = sources_source, TumW, file) %>%
  mutate(number = str_replace(number, "A-KN ", "")) %>%
  separate_longer_delim(number, ", ")

table_data <-
  read_csv("data/inventory_klosterneuburg.csv") %>% 
  mutate(
    inv_a = str_glue("A.{page_a}.{number_a}"),
    inv_b = str_glue("B.{page_b}.{number_b}"),
    inv_c = str_glue("C{volume_c}.{page_c}.{number_c}"),
    inv_e = str_glue("E.{page_e}.{number_e}")
  ) %>% 
  separate_longer_delim(shelfmark, delim = " | ") %>% 
  left_join(
    works %>% select(inv_a = number, TumW_a = TumW),
    by = "inv_a"
  ) %>%
  left_join(
    works %>% select(inv_b = number, TumW_b = TumW),
    by = "inv_b"
  ) %>%
  left_join(
    works %>% select(inv_c = number, TumW_c = TumW),
    by = "inv_c"
  ) %>%
  left_join(
    works %>% select(inv_e = number, TumW_e = TumW),
    by = "inv_e"
  ) %>%
  left_join(
    works %>% select(shelfmark = number, TumW_s = TumW),
    by = "shelfmark"
  ) %>% 
  rowwise() %>%
  mutate(
    is_error_a = any(
      !is.na(shelfmark) &
        is.na(TumW_s),
      is.na(shelfmark) &
        !is.na(page_a) &
        is.na(TumW_a),
      is.na(shelfmark) &
        !is.na(page_b) &
        is.na(TumW_b),
      is.na(shelfmark) &
        !is.na(page_c) &
        is.na(TumW_c),
      is.na(shelfmark) &
        !is.na(page_e) &
        is.na(TumW_e)
    ),
    is_error_b = n_distinct(c(TumW_s, TumW_a, TumW_b,
                              TumW_c, TumW_e), na.rm = TRUE) != 1,
    is_error = is_error_a | is_error_b,
    TumW = coalesce(TumW_s, TumW_a, TumW_b, TumW_c, TumW_e)
  ) %>%
  left_join(
    works %>% distinct(TumW, file),
    by = "TumW"
  ) %>%
  mutate(TumW = str_glue("[{TumW}](/groups/{file}.html#work-{TumW})"))

if (any(table_data$is_error)) {
  print(table_data %>% filter(is_error))
  error("Problems found in A-KN inventory")
}

n_works_a <- 
  table_data %>%
  filter(!is.na(page_a)) %>%
  distinct(page_a, number_a) %>%
  nrow()

n_works_b <- 
  table_data %>%
  filter(!is.na(page_b)) %>%
  distinct(page_b, number_b) %>%
  nrow()

n_works_c <- 
  table_data %>%
  filter(!is.na(page_c)) %>%
  distinct(volume_c, page_c, number_c) %>%
  nrow()

n_works_e <- 
  table_data %>%
  filter(!is.na(page_e)) %>%
  distinct(page_e, number_e) %>%
  nrow()

n_works_extant <- 
  table_data %>%
  filter(!is.na(shelfmark)) %>%
  distinct(shelfmark) %>%
  nrow()
```

The historic inventories of Stift Klosterneuburg [@KlosterneuburgInvA; @KlosterneuburgInvB; KlosterneuburgInvC; KlosterneuburgInvE] contain `{r} n_works_a`, `{r} n_works_b`, `{r} n_works_c`, and `{r} n_works_e` entries describing Tůma's works, respectively. However, only `{r} n_works_extant` works are extant.

```{r A-KN table}
#| echo: false
#| output: asis

table_data %>% 
  select(!c(inv_a:TumW_s, contains("is_error"), file)) %>%
  gt() %>%
  tab_spanner("inventory A", columns = ends_with("_a")) %>% 
  tab_spanner("inventory B", columns = ends_with("_b")) %>% 
  tab_spanner("inventory C", columns = ends_with("_c")) %>% 
  tab_spanner("inventory E", columns = ends_with("_e")) %>% 
  cols_label(
    starts_with("volume") ~ "vol.",
    starts_with("page") ~ "p.",
    starts_with("number") ~ "no."
  ) %>%
  cols_align("right") %>% 
  fmt_markdown(columns = TumW) %>% 
  sub_missing(missing_text = "") %>%
  tab_options(
    column_labels.font.weight = "bold",
    table_body.hlines.style = "none"
  )
```


### @MelkInv

```{r Melk}
#| echo: false
#| output: asis
print_inventory(
  "MelkInv",
  pattern = "vol. (\\w+), no. (\\w+)",
  cols = c("vol.", "no.")
)
```


### @RajhradInvA

```{r Rajhrad A}
#| echo: false
#| output: asis
print_inventory(
  "RajhradInvA",
  pattern = "p. (\\w+), no. (\\w+)",
  cols = c("p", "no.")
)
```


### @RajhradInvB

```{r Rajhrad B}
#| echo: false
#| output: asis
print_inventory(
  "RajhradInvB",
  pattern = "p. (\\w+), no. (\\w+)",
  cols = c("p", "no.")
)
```



## Modern

### @Bardos1980

```{r Bardos 1980}
#| echo: false
#| output: asis
print_inventory(
  "Bardos1980",
  pattern = "p. (\\w+), no. ([\\w/]+)",
  cols = c("p.", "no.")
)
```


### @Pulkert1973

```{r Pulkert 1973}
#| echo: false
#| output: asis
print_inventory(
  "Pulkert1973",
  pattern = "p. (\\w+), no. ([\\w/]+)",
  cols = c("p.", "no.")
)
```


### @Riedel1979

```{r Riedel 1979}
#| echo: false
#| output: asis
print_inventory(
  "Riedel1979",
  pattern = "p. (\\w+), no. (\\w+)",
  cols = c("p.", "no.")
)
```


### @Sherman2001

```{r Sherman 2001}
#| echo: false
#| output: asis
print_inventory(
  "Sherman2001",
  pattern = "p. (\\w+), no. (\\w+)",
  cols = c("p.", "no.")
)
```


### @Stefan1985

```{r Stefan 1985}
#| echo: false
#| output: asis
print_inventory(
  "Stefan1985",
  pattern = "p. (\\w+), no. (\\w+)",
  cols = c("p.", "no.")
)
```
