---
output: html_document
editor_options: 
  chunk_output_type: console
format:
  html:
    html-table-processing: none
---

# Inventories {.unnumbered}

```{r}
#| include: false
library(tidyverse)
library(gt)
source("script/utils.R")
options(readr.show_col_types = FALSE)
```

## Stift Herzogenburg

```{r}
#| echo: false

works <-
  read_rds("data_generated/works.rds") %>% 
  unnest(sources, names_sep = "_") %>% 
  filter(str_starts(sources_source, "A-H ")) %>%
  left_join(
    read_csv("data/catalogue_overview.csv") %>% distinct(group, file),
    by = "group"
  ) %>%
  unite(group:number, col = "TumW", sep = ".", na.rm = TRUE) %>%
  select(number = sources_source, TumW, file) %>%
  mutate(number = str_replace(number, "A-H ", "")) %>%
  separate_longer_delim(number, ", ")


table_data <-
  read_csv("data/inventory_herzogenburg_works.csv") %>% 
  mutate(
    inv_a = str_glue("A.{section_1751}.{number_1751}"),
    inv_b = str_glue("B.{section_1774}.{number_1774}")
  ) %>%
  separate_longer_delim(shelfmark, delim = " | ") %>% 
  left_join(
    works %>% select(inv_a = number, TumW_a = TumW),
    by = "inv_a"
  ) %>%
  left_join(
    works %>% select(inv_b = number, TumW_b = TumW),
    by = "inv_b"
  ) %>%
  left_join(
    works %>% select(shelfmark = number, TumW_s = TumW),
    by = "shelfmark"
  ) %>%
  rowwise() %>%
  mutate(
    is_error = any(
      !is.na(shelfmark) &
        is.na(TumW_s),
      is.na(shelfmark) &
        !is.na(section_1751) &
        is.na(TumW_a),
      is.na(shelfmark) &
        !is.na(section_1774) &
        is.na(TumW_b),
      is.na(shelfmark) &
        !is.na(section_1751) &
        !is.na(section_1774) &
        TumW_a != TumW_b
    )
  ) %>%
  mutate(TumW = coalesce(TumW_s, TumW_a, TumW_b)) %>%
  left_join(
    works %>% distinct(TumW, file),
    by = "TumW"
  ) %>%
  mutate(TumW = str_glue("[{TumW}](/groups/{file}.html#work-{TumW})"))

if (any(table_data$is_error)) {
  print(table_data %>% filter(is_error))
  error("Problems found in A-H inventory")
}

n_works_1751 <- 
  table_data %>%
  filter(!is.na(section_1751)) %>%
  distinct(section_1751, page_1751, number_1751) %>%
  nrow()

n_works_1774 <- 
  table_data %>%
  filter(!is.na(section_1751)) %>%
  distinct(section_1751, page_1751, number_1751) %>%
  nrow()

n_works_extant <- 
  table_data %>%
  filter(!is.na(shelfmark)) %>%
  distinct(shelfmark) %>%
  nrow()
```

The two historic inventories of Stift Herzogenburg [@HerzogenburgInvA; @HerzogenburgInvB] contain `{r} n_works_1751` and `{r} n_works_1774` entries describing Tůma's works, respectively. However, only `{r} n_works_extant` works are extant.

```{r}
#| echo: false
#| output: asis

table_data %>% 
  select(!c(inv_a:TumW_s, is_error, file)) %>%
  gt() %>%
  tab_spanner("inventory 1751 (A)", columns = ends_with("1751")) %>% 
  tab_spanner("inventory 1774 (B)", columns = ends_with("1774")) %>% 
  cols_label(
    starts_with("section") ~ "section",
    starts_with("page") ~ "p.",
    starts_with("number") ~ "no."
  ) %>%
  cols_align("right") %>% 
  fmt_markdown(columns = TumW) %>% 
  sub_missing(missing_text = "") %>%
  tab_options(
    column_labels.font.weight = "bold",
    table_body.hlines.style = "none"
  )
```

In the table above, sections in the 1751 inventory have been consecutively numbered as follows:

```{r}
#| echo: false
#| output: asis

read_csv("data/inventory_herzogenburg_1751.csv") %>% 
  unite(from, to, col = "pp.", sep = "–") %>% 
  gt() %>%
  cols_align("right", columns = "pp.") %>%
  sub_missing(missing_text = "") %>%
  tab_options(
    column_labels.font.weight = "bold",
    table_body.hlines.style = "none"
  )
```

Likewise, sections in the 1774 inventory have been consecutively numbered as follows:

```{r}
#| echo: false
#| output: asis

read_csv("data/inventory_herzogenburg_1774.csv") %>% 
  unite(from, to, col = "fol.", sep = "–") %>% 
  gt() %>%
  cols_width("fol." ~ px(90)) %>%
  cols_align("right", columns = "fol.") %>%
  sub_missing(missing_text = "") %>%
  tab_options(
    column_labels.font.weight = "bold",
    table_body.hlines.style = "none"
  )
```
